Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/model.tex
add comment

Note $t_j$ is the \textit{local} time of the firm, not the global time, so the reputation score is the sliding window average of the last $M$ times that firm $j$ was selected by the agents.\swcomment{define ``calendar time'' and ``local time'' formally... don't think the current reputation defn makes sense} The warm start of $k$ rounds allows this reputation score to be well-defined once the "competition game" begins. In our model the agents deterministically choose the firm with the higher reputation score and ties are broken uniformly at random.

>>>>

Note $t_j$ is the \textit{local} time of the firm, not the global time, so the reputation score is the sliding window average of the last $M$ times that firm $j$ was selected by the agents.\swcomment{define ``calendar time'' and ``local time'' formally... don't think the current reputation defn makes sense} \gacomment{yea, good point. Should define local time formally} The warm start of $k$ rounds allows this reputation score to be well-defined once the "competition game" begins. In our model the agents deterministically choose the firm with the higher reputation score and ties are broken uniformly at random.
